Resurgence of modified Bessel functions of second kind

### 2022-07-13 modified bessel.tex
general thimbles integrals
Jot down notes on dihedral group action
From tea conversation with Maxim.

The modified Bessel function of the second kind $K_\mu(z)$ is a solution of the equation
\begin{equation}\label{Bessel_nu}
w''+\frac{w'}{z}-w-\frac{\mu^2}{z^2}=0
\end{equation}
such that $K_{\mu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$\footnote{A system of solution of Bessel equation is given by $I_\mu(z)$ and $K_\mu(z)$. In particular, their asymptotic behaviour as $z\to\infty$ is given by \begin{align}
\tilde{I}_\mu(z)&=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\mu\right)_k\left(\frac{1}{2}+\mu\right)_k}{2^kk!}z^{-k}\\
\tilde{K}_{\mu}(z)&=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\mu\right)_k\left(\frac{1}{2}+\mu\right)_k}{(-2)^kk!}z^{-k}
\end{align}}. It has a branch point at $z=0$ for every $\mu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$. 
\subsection{Differential equation}
From the general theory of ODE, the formal integral solution of \eqref{Bessel_nu} is two parameters family 
\begin{equation}
\tilde{w}(z)=U_1e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)+U_2e^{z}z^{-1/2}\tilde{w}_{\mu,-}(z)
\end{equation} 
where $\tilde{w}_{\mu,\pm}=\sum_{j\geq 0}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
\begin{align*}
\tilde{w}_{\mu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_{\mu,+}}{4z^2}-\frac{\mu^2}{z^2}\tilde{w}_{\mu,+}=0\\
\tilde{w}_{\mu,-}''+2\tilde{w}_{\mu,-}'+\frac{\tilde{w}_{\mu,-}}{4z^2}-\frac{\mu^2}{z^2}\tilde{w}_{\mu,-}=0
\end{align*} 
In particular, $\tilde{K}_{\mu}(z)=\sqrt{\frac{\pi}{2}}U_1e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)$ and $\tilde{I}_\mu(z)=\frac{1}{\sqrt{2\pi}}U_2 e^zz^{-1/2}\tilde{w}_{\mu,-}(z)$ (we assume $a_{\pm,0}=1$) for some constants $U_1, U_2$. We now compute the Borel transform of $\tilde{w}_+(z)$\footnote{We do not consider constant term of $\tilde{w}_{\mu,\pm}$, i.e. $\mathcal{B}:\C[\![z^{-1}]\!]\to \C[\zeta]$.}: it is a solution of 
\begin{align*}
&\zeta^2\hat{w}_{\mu,+}+2t\hat{w}_{\mu,+}+\left(\frac{1}{4}-\nu^2\right)\int_0^{\zeta}(\zeta-s)\hat{w}_{\nu,+}(s)ds=0 &\\
&\zeta^2\hat{w}_{\mu,+}''+2\zeta\hat{w}_+''+4\zeta\hat{w}_{\mu,+}'+\left(\frac{9}{4}-\mu^2\right)\hat{w}_{\mu,+}=0 & \\
&t(1-t)\hat{w}_{\mu,+}''+(2-4t)\hat{w}_{\mu,+}'-\left(\frac{9}{4}-\mu^2\right)\hat{w}_{mu,+}=0 & t=-\frac{\zeta}{2}
\end{align*} 
therefore $\hat{w}_{\mu,+}(\zeta)$ is an hypergeometric function
\begin{equation}
\hat{w}_{\mu,+}(\zeta)=c_{\mu,+} {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\frac{\zeta}{2}\right)
\end{equation}
and it has a branch point singularities at $\zeta=-2$. By the same reasoning, 
\begin{equation}
\hat{w}_{\mu,-}(\zeta)=c_{\mu,-} {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{\zeta}{2}\right)
\end{equation} 
and it has branch point at $\zeta=2$.

@@

Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and for every $\mu\in [0,+\infty)$ let $\nu=x^{\mu-1}+\frac{1}{x^{\mu+1}}dx$, then

@@

In particulr, on the universal cover $\pi\colon\tilde{C}\to \C^*$ setting $x=e^u$ 
\begin{equation}
I(\tfrac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
\end{equation} 
where $K_\mu(z)$ is the second kind modified Bessel function with parameter $\mu$.

@@

Therefore we have shown that Stokes constants are independent on $\mu$ and equal to $\pm 2$.

>>>>

The modified Bessel function of the second kind $K_\mu(z)$ is a solution of the equation
\begin{equation}\label{Bessel_nu}
w''+\frac{w'}{z}-w-\frac{\mu^2}{z^2}w=0
\end{equation}
such that $K_{\mu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$\footnote{A system of solution of Bessel equation is given by $I_\mu(z)$ and $K_\mu(z)$. In particular, their asymptotic behaviour as $z\to\infty$ is given by \begin{align}
\tilde{I}_\mu(z)&=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\mu\right)_k\left(\frac{1}{2}+\mu\right)_k}{2^kk!}z^{-k}\\
\tilde{K}_{\mu}(z)&=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\mu\right)_k\left(\frac{1}{2}+\mu\right)_k}{(-2)^kk!}z^{-k}
\end{align}}. It has a branch point at $z=0$ for every $\mu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$. 
\subsection{Differential equation}
From the general theory of ODE, the formal integral solution of \eqref{Bessel_nu} is two parameters family 
\begin{equation}
\tilde{w}(z)=U_1e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)+U_2e^{z}z^{-1/2}\tilde{w}_{\mu,-}(z)
\end{equation} 
where $\tilde{w}_{\mu,\pm}=\sum_{j\geq 0}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
\begin{align*}
\tilde{w}_{\mu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_{\mu,+}}{4z^2}-\frac{\mu^2}{z^2}\tilde{w}_{\mu,+}=0\\
\tilde{w}_{\mu,-}''+2\tilde{w}_{\mu,-}'+\frac{\tilde{w}_{\mu,-}}{4z^2}-\frac{\mu^2}{z^2}\tilde{w}_{\mu,-}=0
\end{align*} 
In particular, $\tilde{K}_{\mu}(z)=\sqrt{\frac{\pi}{2}}U_1e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)$ and $\tilde{I}_\mu(z)=\frac{1}{\sqrt{2\pi}}U_2 e^zz^{-1/2}\tilde{w}_{\mu,-}(z)$ (we assume $a_{\pm,0}=1$) for some constants $U_1, U_2$. We now compute the Borel transform of $\tilde{w}_+(z)$\footnote{We do not consider constant term of $\tilde{w}_{\mu,\pm}$, i.e. $\mathcal{B}:\C[\![z^{-1}]\!]\to \C[\zeta]$.}: it is a solution of 
\begin{align*}
&\zeta^2\hat{w}_{\mu,+}+2t\hat{w}_{\mu,+}+\left(\frac{1}{4}-\nu^2\right)\int_0^{\zeta}(\zeta-s)\hat{w}_{\nu,+}(s)ds=0 &\\
&\zeta^2\hat{w}_{\mu,+}''+2\zeta\hat{w}_+''+4\zeta\hat{w}_{\mu,+}'+\left(\frac{9}{4}-\mu^2\right)\hat{w}_{\mu,+}=0 & \\
&t(1-t)\hat{w}_{\mu,+}''+(2-4t)\hat{w}_{\mu,+}'-\left(\frac{9}{4}-\mu^2\right)\hat{w}_{mu,+}=0 & t=-\frac{\zeta}{2}
\end{align*} 
therefore $\hat{w}_{\mu,+}(\zeta)$ is an hypergeometric function
\begin{equation}
\hat{w}_{\mu,+}(\zeta)=c_{\mu,+} {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\frac{\zeta}{2}\right)
\end{equation}
and it has a branch point singularities at $\zeta=-2$. By the same reasoning, 
\begin{equation}
\hat{w}_{\mu,-}(\zeta)=c_{\mu,-} {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{\zeta}{2}\right)
\end{equation} 
and it has branch point at $\zeta=2$.

@@

Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and for every $\mu\in [0,+\infty)$ let $\nu=\left(x^\mu+x^{-\mu}\right) \tfrac{dx}{x}$, then

@@

In particular, on the universal cover $\pi\colon\tilde{C}\to \C^*$ setting $x=e^u$ \textbf{[DLMF, Identity~10.32.9]}
\begin{equation}
I(\tfrac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)\,du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
\end{equation} 
where $K_\mu(z)$ is the second kind modified Bessel function with parameter $\mu$.

@@

Therefore we have shown that Stokes constants are independent on $\mu$ and equal to $\pm 2$.
\subsection{Why the Stokes factors are non-integer}
The infinite dihedral group $D_{2\infty} \isom \Z \ltimes \Z/2\Z$ has a nice action on $\tilde{C}$ that leaves $e^{-z \cosh(u)}$ invariant. The action of $1 \in \Z$ adds $2\pi i$ to the value of $u$, and the actions of $\{\pm 1\} \isom \Z/2$ multiply the value of $u$ by $\pm 1$.

Consider exponential integrals of the form
\[ \langle \Gamma, e^{-z \cosh(u)}\,\alpha\rangle := \int_\Gamma e^{-z \cosh(u)}\,\alpha, \]
where the variety $\tilde{C}$ and the twisting factor $e^{-z \cosh(u)}$ are fixed, while the integration path $\Gamma$ and the twisted 1-form $e^{-z \cosh(u)}\,\alpha$ are allowed to vary. We can apply the action of $D_{2\infty}$ to these integrals by pushing forward the integration contour, or equivalently by pulling back the twisted 1-form. This makes the vector space of exponential integrals into a representation of $D_{2\infty}$.

Let's see what the action does to $I(\tfrac{z}{2}; \mu) = \langle -\infty \to \infty, e^{-z \cosh(u)}\,\nu \rangle$, recalling that $\nu = \cosh(\mu u)\,du$. Pulling $\nu$ back along $1 \in \Z$ gives
\begin{align*}
\cosh(\mu u + 2\pi i \mu)\,du & = \big[\cosh(2\pi i \mu) \cosh(\mu u) + \sinh(2\pi i \mu) \sinh(\mu u)\big]\,du \\
& = \cos(2\pi \mu)\,\nu + i\sin(2\pi \mu) \sinh(\mu u)\,du.
\end{align*}
and pulling it back along $\pm 1 \in \Z/2\Z$ gives $\pm\nu$. Hence, $1 \in \Z$ sends
\[ I(\tfrac{z}{2}; \mu) = 2\int_{-\infty}^{\infty} e^{-z\cosh(u)}\,\nu \]
to
\begin{align*}
& 2\int_{-\infty}^{\infty} e^{-z\cosh(u)} \big[\cos(2\pi \mu)\,\nu + i\sin(2\pi \mu) \sinh(\mu u)\,du\big] \\
& = 2\cos(2\pi \mu) \int_{-\infty}^{\infty} e^{-z\cosh(u)}\,\nu + 2i\sin(2\pi \mu) \int_{-\infty}^{\infty} e^{-z\cosh(u)} \sinh(\mu u)\,du \\
& = \cos(2\pi \mu)\,I(\tfrac{z}{2}; \mu),
\end{align*}
with the second term vanishing in the last step because $\sinh(\mu u)$ is odd. Also, $\pm 1 \in \Z/2\Z$ sends $I(\tfrac{z}{2}; \mu)$ to $\pm I(\tfrac{z}{2}; \mu)$. Now we see that in the space of exponential integrals, considered as a representation of $D_{2\infty}$, the span of $I(\tfrac{z}{2}; \mu)$ is a one-dimensional subrepresentation, giving the character \textbf{[correct word?]}
\begin{align*}
D_{2\infty} & \to \C^\times \\
1 \in \Z & \mapsto \cos(2\pi \mu) \\
\pm 1 \in \Z/2\Z & \mapsto \pm 1.
\end{align*}

\textbf{[The other invariant subspace should be generated by the path $-\infty + \pi i \to \infty + \pi i$.]}

Another way to think of this: if we choose bases for the space of (relative homology classes of) integration paths and the space of (relative cohomology classes of) twisted 1-forms, we can write a period matrix for $\langle\;,\;\rangle$. The entries of the period matrix form a basis for the space of exponential integrals. The action of $D_{2\infty}$ on exponential integrals can be seen as an action on the period matrix. When $D_{2\infty}$ acts on integration paths, it acts on the period matrix by left multiplication; when it acts on 1-forms, it acts on the period matrix by right multiplication. The the left and right action matrices are adjoints with respect to $\langle\;,\;\rangle$. The argument above shows that for well-chosen bases, we can make the action matrices block-diagonal, with two blocks.

When $\mu = 1/n$ for $n \in \N$, the space of integration paths and the space of twisted 1-forms are both $n$-dimensional, and \textbf{[...]}
